Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-07-05 paper/structureScene.tex
update paper
work on intro and section structure

Also, some recent works demonstrate the interest of such approaches for the characterization of human acoustic pleasantness in urban areas \cite{lafayPartI, guyot2005urban, ricciardi2015sound} \gl{What was the lavandier article ?} and the prediction of annoyance due to the traffic \cite{gloaguen}. We believe that those case study are of interest for the signal processing community as they have strong societal impacts and raises interesting research avenues. Unfortunately, those fields of research are still in infancy and consequently very few well built datasets are available for evaluation purposes.

A closely related field of investigation that is relatively more mature is the classification of acoustic scenes whose aim is to predict labels by processing audio data. Despite its lower value, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data processing field for a while, with availability of some well designed evaluation datasets.

@@

The starting scale $\gamma_{1,\min}$ corresponding to some upper bound $\xi_{1,\max}$ on the frequency axis is given by
\begin{equation}
\gamma_{1,\min} =
\left\lfloor Q_1 \log_2 \frac{\xi_1}{\xi_{1,\max}} \right\rceil
\end{equation}
where $\lfloor \cdot \rceil$ denotes a rounding to the nearest integer.

@@

\section{Unsupervised approach}

@@

@@

\section{Supervised approach: support vector machines}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.

VL

>>>>

Also, some recent works demonstrate the interest of such approaches for the characterization of human acoustic pleasantness in urban areas \cite{lafayPartI, guyot2005urban, ricciardi2015sound} and the prediction of annoyance due to the traffic \cite{gloaguen}. We believe that those case study are of interest for the signal processing community as they have strong societal impacts and raises interesting research avenues.

Unfortunately, those fields of research are still in infancy and consequently very few well built datasets are readily available for evaluation purposes for the signal processing community. A closely related field of investigation that is relatively more mature is the classification of acoustic scenes whose aim is to predict labels by processing audio data. Despite being narrower in terms of range of applications, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data processing field for a while, with availability of some well designed evaluation datasets.

Despite the differences, the following question is valid both for the above cited future application and the acoustic scene classification (ASC). How can we efficiently and effectively process large amount of audio data using representations that are both compact, generic in their design and with a large application range ?

The research described in this paper tackles that question by demonstrating the usefulness of two main contributions: 1) the use of the scattering transform allows us to extract discriminative features with almost no parameter optimization and 2) object-based modeling of the acoustic scene based on individual unsupervised clustering of each acoustic scene  allows us to effectively focus the description on areas of interest. Those contributions are extensively described, respectively in Section \ref{sec:scattering} and \ref{sec:object} and evaluated both in an unsupervised setting, \textit{i.e.} acoustic scene similarity (ASS) and in a supervised setting, \textit{i.e.}  acoustic scene classification (ASC), respectively in Section \ref{sec:similarity} and Section \ref{sec:classification}.

paper

@@

The starting scale $\gamma_{1,\min}$ corresponding to some upper bound $\xi_{1,\max}$ on the frequency axis is given by
\begin{equation}
\gamma_{1,\min} =
\left\lfloor Q_1 \log_2 \frac{\xi_1}{\xi_{1,\max}} \right\rceil
\end{equation}
where $\lfloor \cdot \rceil$ denotes a rounding to the nearest integer.
% Advantage over PCA: we keep nonnegativity and the features remain uninterpretable.

@@

\section{Object-based modeling of the scene}

\subsection{Protocol}

\section{Acoustic Scene Similarity}

@@

\section{Acoustic Scene Classification}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.

\subsection{Protocol}

@@
